Probabilistic Forecast Reconciliation

### 2018-06-12 Presentation/ProbForeRec.tex
fixed minor errors

  	  \item Collections of Time Series often characterised by aggregation constraints

@@

        \item Adjusting base forecasts to obtain {\bf reconciled} forecasts in an $n\times 1$ vector $\tilde{\bm y}$

@@

  	The probability triple $\left(\mathfrak{s},\mathcal{F}_{\mathfrak{s}},\tilde{\nu}\right)$ is the reconciles the probability triple $\left(\mathbb{R}^n,\mathcal{F}_{\mathbb{R}^n},\hat{\nu}\right)$ with with respect to $g$ iff

@@

		E_{\bm y}\left[S(\hat{f},\bm{y})\right]<E_{\bm y}\left[S(f,\bm{y})\right]

>>>>

  	  \item Collections of time series often characterised by aggregation constraints

@@

        \item Adjusting base forecasts to obtain coherent {\bf reconciled} forecasts in an $n\times 1$ vector $\tilde{\bm y}$

@@

  	The probability triple $\left(\mathfrak{s},\mathcal{F}_{\mathfrak{s}},\tilde{\nu}\right)$ reconciles the probability triple $\left(\mathbb{R}^n,\mathcal{F}_{\mathbb{R}^n},\hat{\nu}\right)$ with with respect to $g$ iff

@@

		E_{\bm y}\left[LS(\hat{f},\bm{y})\right]<E_{\bm y}\left[LS(f,\bm{y})\right]
